Building a continuous benchmarking ecosystem in bioinformatics

### 2025-07-23 2_second_review/manuscript.tex
Update bibitems for funkyheatmaps, bettr and diataxis; update texttts.

Finally, scientific software management handling is known for its nuances, including abundant dependencies with known incompatibilities and complex installation recipes \cite{droge2023-ax}. Scientific software management is handled via traditional (Linux) package managers (RPMs, DEBs), central software stacks and environment modules (i.e., Lmod), \texttt{conda}, containers (e.g., \texttt{apptainer} or \texttt{Singularity}; \cite{Kurtzer2017-mn}), or read-only network filesystems providing ready-to-use installations (CernVM-FS) \cite{Blomer2013-jk}. Further strategies are under active development: EESSI \cite{droge2023-ax} and the Digital Research Alliance of Canada \cite{Boissonneault2019-wm} are effectively providing multi-purpose, reusable and efficient software installations via CernVM-FS; \texttt{conda} is speeding up their deployment procedures (via \texttt{py-rattler}/\texttt{pixi}) and allowing compilation to Web assembly (to execute code within a web browser); and \texttt{apptainer} (former \texttt{Singularity}) provides rootless containerization suitable for running in scientific clusters.

@@

\bibitem{funkyheatmap}
Cannoodt R, Saelens W. type [;]Available from:
  \url{https://cran.r-project.org/web/packages/funkyheatmap/index.html}.

@@

\bibitem{bettr}
Marini F, Soneson C. type [; 2024]Available from:
  \url{https://www.bioconductor.org/packages/release/bioc/html/bettr.html}.

@@

\bibitem{ProcidaUnknown-vf}
Procida D. Diátaxis;.
\newblock Available from: \url{https://diataxis.fr/}.

>>>>

Finally, scientific software management handling is known for its nuances, including abundant dependencies with known incompatibilities and complex installation recipes \cite{droge2023-ax}. Scientific software management is handled via traditional (Linux) package managers (RPMs, DEBs), automated and reproducible installs (such as \texttt{EasyBuild} \cite{Hoste2012-gg} or \texttt{Spack} \cite{Gamblin2015-ll}), central software stacks and environment modules (i.e., \texttt{Lmod}), \texttt{conda}, containers (e.g., \texttt{apptainer} or \texttt{Singularity}; \cite{Kurtzer2017-mn}), or read-only network filesystems providing ready-to-use installations (\texttt{CernVM-FS}) \cite{Blomer2013-jk}. Further strategies are under active development: EESSI \cite{droge2023-ax} and the Digital Research Alliance of Canada \cite{Boissonneault2019-wm} are effectively providing multi-purpose, reusable and efficient software installations via \texttt{CernVM-FS}; \texttt{conda} is speeding up their deployment procedures (via \texttt{py-rattler}/\texttt{pixi}) and allowing compilation to Web assembly (to execute code within a web browser); and \texttt{apptainer} (former \texttt{Singularity}) provides rootless containerization suitable for running in scientific clusters.

@@

\bibitem{funkyheatmap}
Cannoodt R, Saelens W. 
\newblock funkyheatmap: Generating Funky Heatmaps for Data Frames
\newblock Available from \url{https://cran.r-project.org/web/packages/funkyheatmap/index.html}.

@@

\bibitem{bettr}
Marini F, Soneson C. 
\newblock bettr: A Better Way To Explore What Is Best
\newblock Available from: \url{https://www.bioconductor.org/packages/release/bioc/html/bettr.html}.

@@

\bibitem{ProcidaUnknown-vf}
Procida D. 
\newblock Diátaxis: A systematic approach to technical documentation authoring.
\newblock Available from: \url{https://diataxis.fr/}.
